|

### 2020-05-21 paper/Manuscript.Rmd
Try to improve structure

abstract: |
  The social sciences are amidst a paradigm shift towards open science. In part,
  this transition has been fueled by cases of scientific fraud and increasing
  awareness of questionable research practices and failed replications. However,
  open science is not
  merely a cure (or punishment) for this crisis - it is also an opportunity.
  Technological advances enable researchers to more easily conduct reliable,
  cumulative, collaborative science. Capitalizing on these advances has the
  potential to accelerate scientific progress. This tutorial paper introduces a
  workflow for open reproducible code in science (WORCS). WORCS is a 
  step-by-step procedure that researchers can follow to make an entire project
  Open and Reproducible. It is based on best practices, and can be used either
  in parallel to, or in absence of, top-down requirements by journals. WORCS
  lowers the threshold for adopting an open science workflow by providing this
  tutorial, along with an R-package with user-friendly support functions, and an
  RStudio project template.

@@

Many individual researchers are motivated to adopt best practices for open
science and enjoy these benefits. And yet, the question of "how" to 
adopt open science practices can be daunting. Making the transition effectively
requires researchers to become knowledgeable about different open science 
challenges and solutions, and to become proficient with new and unfamiliar tools.
This paper is designed to ease that transition by providing a simple workflow 
that meets most requirements open science, based on best practices, and 
supported by user-friendly software in R: The Worfkflow for Open Reproducible 
Code in Science (WORCS). WORCS is a lightweight approach to open science and
computational reproducibility. The workflow (Figure <!--\@ref(fig:workflow)-->) 
constitutes a step-by-step procedure that researchers can follow to make a 
research project Open and Reproducible. WORCS is compatible with open science
requirements already implemented by journals and institutions, and will help 
fulfill them. It can also be used to produce work in accordance with best 
practices in the absence of top-down support. The WORCS workflow is supported by
an R-package with user-friendly support functions, and an RStudio project
template that is, effectively, a "one click solution". This paper introduces
the WORCS workflow, discusses how it meets best practices for open science, and
illustrates the use of the `worcs` package.

@@

WORCS meets the TOP-guidelines in a way that is amenable to the 
FAIR Guiding Principles for scientific data management and stewardship [@wilkinsonFAIRGuidingPrinciples2016a]. These principles advocate that research
data should be Findable, Accessible, Interoperable and Reusable. However, they are
increasingly applied as a standard for 
to other types of research output as well
[@lamprechtFAIRPrinciplesResearch2019].
WORCS helps users meet the FAIR principles by making all research objects -
including (origina) data and code - accessible in a (public) repository. 
The `worcs` package additionally
facilitates meeting the FAIR principles in several ways. First, each `worcs`
project has a YAML file (https://yaml.org/) that lists the research objects in
the project, which will allow web crawlers 
to index `worcs` projects. Second, a codebook is automatically generated for
each data file stored
using `open_data()` or `closed_data()`. We encourage users to elaborate on the
default codebook by adding
variable description and categories, which might - in the future - enable
indexing data by topic area. 
Incidentally, `worcs` is itself an example of FAIR research software [see @lamprechtFAIRPrinciplesResearch2019 and https://fair-software.eu/]. It is hosted on a public version controlled repository ('GitHub'), it has an open source licence (GPL v3.0), is registered in a community registry (CRAN), it enables the citation of the software (using the `citation("worcs")` command, or by citing this paper), and followed the CII Best Practices software quality checklist during development.

Sharing all research output also provides a proper basis for research evaluation
according to the San Francisco Declaration on Research Assessment (DORA;
https://sfdora.org/), which plays an increasing role in grant funding, hiring, 
and promotion procedures. Direct access to research objects allows stakeholders
to evaluate research quality based on content rather than relying on spurious
surrogate indicators like journal impact factors, conference rankings, and
h-indexes. The detailed version control and commit tracking of 'GitHub' and
similar platforms furthermore make it possible to assess the relative
contributions made by different researchers.

@@

## Existing solutions

<!-- AL: Similar to my comment on the title, in this section it needs to make clear which scope of related work it covers. For example, in the life sciences there has also been a lot of work on practices for increasing reproducibility, with automated workflows, containerization, Research Objects, provenance protocols, and a lot more. I don't think it's necessary for this paper to discuss this, but that is under the provision that it defines its scope better. --> 
## Prerequisites

@@

@@

# The workflow 
<!-- AL: Agreeing with LB's ealier comment, it would be good to discuss this overall workflow before going into the details. -->

@@

In this tutorial paper, we have presented a workflow for open reproducible code in science. The workflow aims to lower the threshold for grass-roots adoption of open science principles. It is accompanied by an R-package with convenience functions, and a WORCS project template for RStudio. This relatively light-weight workflow meets most of the requirements for open science, as detailed in the TOP-guidelines. However, several limitations and issues for future development remain.

One potential challenge is the learning curve associated with the tools outlined in this paper. Learning to work with R, Rmarkdown, and Git/GitHub requires an initial time investment. The amount of time required is reduced by the availability of tutorials, such as this one, and other tutorials cited throughout this document. Moreover, the time investment tends to pay off. Working with R opens the door to many cutting edge analysis techniques. Working with Rmarkdown saves time and prevents mistakes by avoiding tedious copying of results into a text document. Working with Git/GitHub keeps projects organized, prevents accidental loss of work, enables integrating changes by collaborators in a non-destructive manner, and ensures that entire research projects are archived and can be accessed or copied by third parties. Thus, the time investment is eminently worthwhile.

>>>>

abstract: |
  The social sciences are amidst a paradigm shift towards open science. In part,
  this transition has been fueled by cases of scientific fraud and increasing
  awareness of questionable research practices and failed replications. However,
  open science is not
  merely a cure (or punishment) for this crisis - it is also an opportunity.
  Technological advances enable researchers to more easily conduct reliable,
  cumulative, collaborative science. Capitalizing on these advances has the
  potential to accelerate scientific progress. This tutorial paper introduces a
  workflow for open reproducible code in science (WORCS). WORCS is a 
  step-by-step procedure that researchers can follow to make an entire project
  open and reproducible. It is based on best practices, and can be used either
  in parallel to, or in absence of, top-down requirements by journals. WORCS
  lowers the threshold for adopting an open science workflow by providing this
  tutorial, along with an R-package with user-friendly support functions, and an
  RStudio project template.

@@

Many individual researchers are motivated to adopt best practices for open
science and enjoy these benefits. And yet, the question of "how" to 
adopt open science practices can be daunting. Making the transition effectively
requires researchers to become knowledgeable about different open science 
challenges and solutions, and to become proficient with new and unfamiliar tools.
This paper is designed to ease that transition by providing a simple workflow 
that meets most requirements open science, based on best practices, and 
supported by user-friendly software in R: The Worfkflow for Open Reproducible 
Code in Science (WORCS). WORCS is a lightweight approach to open science and
computational reproducibility. The workflow (Figure <!--\@ref(fig:workflow)-->) 
constitutes a step-by-step procedure that researchers can follow to make a 
research project open and reproducible. WORCS is compatible with open science
requirements already implemented by journals and institutions, and will help 
fulfill them. It can also be used to produce work in accordance with best 
practices in the absence of top-down support. Although the principles underlying
the WORCS procedure are universal, they have been implemented for R users in the
R-package `worcs`, which offers an RStudio project template that is, effectively,
a "one click solution". This paper introduces the WORCS workflow, discusses how
it meets best practices for open science, and illustrates the use of the `worcs`
package.

@@

WORCS meets the TOP-guidelines in a way that is amenable to the 
FAIR Guiding Principles for scientific data management and stewardship [@wilkinsonFAIRGuidingPrinciples2016a]. These principles advocate that research
data should be Findable, Accessible, Interoperable and Reusable. They are
increasingly applied as a standard for other types of research output as well
[@lamprechtFAIRPrinciplesResearch2019].
WORCS helps users meet the FAIR principles by making all research objects -
including data and code - accessible in a repository that can be made public. 
The `worcs` package additionally
facilitates meeting the FAIR principles in several ways. First, each `worcs`
project has a YAML file (https://yaml.org/) that lists the research objects in
the project, which will allow web crawlers 
to index `worcs` projects. Second, a codebook is automatically generated for
each data file stored
using `open_data()` or `closed_data()`. We encourage users to elaborate on the
default codebook by adding
variable description and categories, which might - in the future - enable
indexing data by topic area. 
Incidentally, `worcs` is itself an example of FAIR research software [see @lamprechtFAIRPrinciplesResearch2019 and https://fair-software.eu/]. It is 
hosted on the public version controlled repository 'GitHub', it has an open
source licence (GPL v3.0), is registered in a community registry (CRAN), it
enables the citation of the software (using the `citation("worcs")` command, or
by citing this paper), and followed the CII Best Practices software quality
checklist during development.

Sharing all research objects, as advocated in WORCS, also provides a proper
basis for research evaluation
according to the San Francisco Declaration on Research Assessment (DORA;
https://sfdora.org/), which plays an increasing role in grant funding, hiring, 
and promotion procedures. Direct access to research objects allows stakeholders
to evaluate research quality based on content rather than relying on spurious
surrogate indicators like journal impact factors, conference rankings, and
h-indexes. The detailed version control and commit tracking of 'GitHub' and
similar platforms furthermore make it possible to assess the relative
contributions made by different researchers.

@@

## Prerequisites

@@

# Introducing the workflow 
<!-- AL: Agreeing with LB's ealier comment, it would be good to discuss this overall workflow before going into the details. -->

@@

@@

In this tutorial paper, we have presented a workflow for open reproducible code in science. The workflow aims to lower the threshold for grass-roots adoption of open science principles. It is accompanied by an R-package with convenience functions, and a WORCS project template for RStudio. This relatively light-weight workflow meets most of the requirements for open science, as detailed in the TOP-guidelines.

## Differences from existing solutions

<!-- AL: Similar to my comment on the title, in this section it needs to make clear which scope of related work it covers. For example, in the life sciences there has also been a lot of work on practices for increasing reproducibility, with automated workflows, containerization, Research Objects, provenance protocols, and a lot more. I don't think it's necessary for this paper to discuss this, but that is under the provision that it defines its scope better. -->

## Limitations

WORCS is intended to substantially reduce the threshold for adopting best 
practices in open and reproducible research. However, several limitations and
issues for future development remain. One potential challenge is the learning
curve associated with the tools outlined in this paper. Learning to work with R,
Rmarkdown, and Git/GitHub requires an initial time investment. The amount of
time required is reduced by the availability of tutorials, such as this one, and
other tutorials cited throughout this document. Moreover, the time investment
tends to pay off. Working with R opens the door to many cutting edge analysis
techniques. Working with Rmarkdown saves time and prevents mistakes by avoiding
tedious copying of results into a text document. Working with Git/GitHub keeps
projects organized, prevents accidental loss of work, enables integrating
changes by collaborators in a non-destructive manner, and ensures that entire
research projects are archived and can be accessed or copied by third parties.
Thus, the time investment is eminently worthwhile.
